Maaslin runs

### 2019-08-07 maaslinruns.Rmd
Fixing maaslin runs

```{r data}
pseq.genus <- import_filter_data("data/phfinrisk_centrifuge_genus_d50k_2019-06-02.rds")
pseq.species <- import_filter_data("data/phfinrisk_centrifuge_species_all_drop50k_2018-11-30_2019-06-03.RDs")
```

@@

@@

```{r process genus}
pseq.genus.core <- core(pseq.genus, detection = 0.001, prevalence = 0.01)
pseq.genus.core.viruses.names <- taxa(pseq.genus.core) %>% mygrep(word = "virus$", complement = TRUE)
pseq.genus.core.pruned <- prune_taxa(pseq.genus.core.viruses.names, pseq.genus.core)
```

```{r maaslin runs, results = 'hide', eval  = FALSE} 
ret <- mclapply(var.CL.comb, function(x)
    maaslinwrapper(pseq = pseq.genus.core.pruned,
                   looped = var.BP,
                   forced = x,
                   taxa = taxa(pseq.genus.core.pruned),
                   tempstr = sprintf("%%s/maaslinruns/maaslinruns/%%s_%s", paste0(x, collapse = "_"))),
    mc.cores = length(var.CL.comb))
```

@@

```{r adding third, eval = FALSE}
ret3rd <- mclapply(var.CL.comb3rd, function(x)
    maaslinwrapper(pseq = pseq.genus.core.pruned,
                   looped = var.BP,
                   forced = x,
                   taxa = taxa(pseq.genus.core.pruned),
                   tempstr = sprintf("%%s/maaslinruns/maaslinruns/%%s_%s", paste0(x, collapse = "_"))),
    mc.cores = length(var.CL.comb3rd))

>>>>

```{r data}
pseq.genus <- import_filter_data("data/phfinrisk_centrifuge_genus_d50k_2019-06-02.rds")
```

@@

```{r defining genus core}
pseq.genus.core <- microbiome::transform(pseq.genus, "compositional") %>%
    core(detection = 0.0001, prevalence = 0.01)
```

@@

```{r maaslin runs, results = 'hide', eval  = FALSE} 
ret <- mclapply(var.CL.comb, function(x)
    maaslinwrapper(pseq = pseq.genus.core,
                   looped = var.BP,
                   forced = x,
                   taxa = taxa(pseq.genus.core),
                   tempstr = sprintf("%%s/maaslinruns/maaslinruns/%%s_%s", paste0(x, collapse = "_"))),
    mc.cores = length(var.CL.comb))
```

@@

```{r adding third, eval = FALSE}
ret3rd <- mclapply(var.CL.comb3rd, function(x)
    maaslinwrapper(pseq = pseq.genus.core,
                   looped = var.BP,
                   forced = x,
                   taxa = taxa(pseq.genus.core),
                   tempstr = sprintf("%%s/maaslinruns/maaslinruns/%%s_%s", paste0(x, collapse = "_"))),
    mc.cores = length(var.CL.comb3rd))
